### 2017-05-18 paper/paper.tex
style
possibly

\begin{definition}
Let proposition $\cs{n}$ be: $\lf{n}$ is surjective.
\end{definition}

@@

\begin{remark}
Vu's code: $\cs6$ is \emph{likely} true \\
(1\% complete, 10 days elapsed, 3 years left).
\end{remark}

>>>>

\begin{definition}
Let proposition $\cs{n}$ be ``$\lf{n}$ is surjective''.
\end{definition}

@@

\begin{remark}
Vu's code: $\cs6$ is \emph{possibly} true \\
(1\% complete, 10 days elapsed, 3 years left).
\end{remark}
